Fishery Markets and Large-Scale Marine Conservation

### 2019-05-30 docs/old_ms/PIPA_Palau022819.tex
Added all files

We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}). Treated vessels traveled less, with fishing events occurring closer to shore and closer to port following PIPA implementation. These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$). We do not observe a statistically significant increase in fishing hours on the high seas.

The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in Kiribati and PNA waters decreases suggests that these vessels have re-distributed elsewhere. This is consistent with the eventual decrease in crowding meassures.

@@

The crowding effect combined with the reduction of hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy access fees from PNA countries. To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by all PNA countries by each group of vessels (Fig. \ref{fig:all_PS_VDS_year}). In this case we look at all 313 vessels, but continue to group them as treated (n = 64) and control (n = 28) vessels, as well as other vessels (n = 221). We find that the treated vessels spent 2,310 less days in PNA waters when comparing their values for 2015 and 2016, while control and other vessels increased their activities in PNA waters by 5,489 and 4,447 days for the same period, respectively (Fig. \ref{fig:included_PS_VDS_year_DiD}). The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD at an average price of \$12,000 USD per vessel-day. Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig. \ref{fig:all_PS_VDS_cty_year}). Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allcoation to PNA waters at just 10,026 vessel-days. This is 2,526 vessel-days lower (\~\$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}). % Do you think we need to come up with an identification strategy for this?. I think a simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort, right? Current DiD estimate of these data suggests a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects. These values would represent forgone profits of 104 to 88 million USD. Again, this is if the treated vessels were allowed to maintain an upward sloping trend as observed with the control. I am also not sure if this trend is true, or just an artifact of GFW. Could we de-trend it first so that both lines are flat before, and only treated vessels show a decrease? In that setting we can then do a DiD and calculate the gap more accurately.

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_year.pdf}
	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all countries by treated, control, and excluded vessels.}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by group of vessels.}
\end{figure}

We compliment our analysis of change in observed vessel-days by looking at country-level data. Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig. \ref{fig:revenues}A). We find that by 2016, Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD. We then calculate total annual revenues to all PNA members (Fig. \ref{fig:revenues}B). To estimate what would have been the total revenue to PNA members, we use a local polynomial regression fit to obtain a trend line for the total revenues between 2008 and 2015, and extrapolate the trend to obtain an expected value for 2016. Our model suggests that total revenues to all PNA members in 2016 should be in the order of \$463.5 million USD, but the FFA data show only \$423.5 million, suggesting that potential losses to the entire PNA are in the order of \$40 million USD.

\begin{figure}
\centering
	\includegraphics{img/revenues.pdf}
	\caption{\label{fig:revenues}Financial indicators for PNA countries. A) Revenue from fishing licenses fees, B) Total annual revenues for all 9 PNA countries with dashed line showing the local polynomial regression fit to the 2008 - 2015 data and the red dot representing the prediction from this regression. Vertical dashed line in both plots denotes implementation of PIPA.}
\end{figure}

Catches for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig. \ref{fig:catches}). Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease). Similar decreases were observed for The Federal States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%). In contrast, Tokelau (due south of Kiribati) showed a 22.3\% increase in catches over the same period.

@@

Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort. We find a short-term crowding effect after the implementation of the protected area. Behavioral analysis shows that the implementation of PIPA had little effect on the total fishing effort exerted by purse seiners. This, combined with our analysis of crowding effects that eventually return to pre-implementation levels, suggests that vessels redistribute elsewhere. Our analysis suggests that vessels that fish elsewhere represent a loss in profits of around \$27.7 million USD to Kiribati. A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD. Here, we discuss the implications of our findings and possible shortcommings in our analyses.

@@

A major shortcoming of our analysis is that we do not observe catches or revenues at he vessel level, which ultimately are the factors that guide the decision making process of profit-maximizing agents. Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact. An additional factor that we are yet to test is the change in non-fishing hours spent at sea. It is plausible that fishing hours remain constant, but vessels have to increase search time. Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch. Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours. However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.

A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in large losses to countries. We also show that spatial closures lead to short-term crowding effects, which causes vessels to redistribute to areas close by. Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere. While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable mechanisms that would compensate losses and incentivize marine conservation.

@@

Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels. These broadcast messages can be received by satellites and land-based antennas. GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer what type and location of fishing events \citep{kroodsma_2018}.

@@

\subsection{Analyses}

@@

If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve. The implementation would lead to an increase in these measures, which,  if vessels avoid crowding, should then come back down. We therefore expect to have three inflection points: 1) in the transition between no trend and initial crowding due to MPA implementation, 2) When the crowding has reached its maximum and starts to decrease, and 3) when the decrease levels off, pressumably to pre-MPA levels. For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by centering our time series of crowding indices on the day of implementation. Our explanatory variable is therefore the number of months ($M$) before or after the implementation. For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1, and Feb of 2015 would receive a value of 1.

\begin{figure}
\begin{align}
y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \epsilon_t
\label{eqn:sp_corr}
\end{align}
\end{figure}

@@

We then focus on identifying the response of vessels to the PIPA closure. We use daily fishing and non-fishing hours, daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port(km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest. We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach. Our main specification is the following:

@@

Where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$. A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group. $\alpha$ is the standard intercept term, $beta_1$ captures the temporal trend, $beta_2$ captures the initial difference between treated and control groups, and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect. Finally, $phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions. We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.

@@

Information about FFA reports here

@@

@@

\begin{figure}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. Countries that belong to the PNA are shown in blue, while empty polygons indicates all others. A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/all_panels.pdf}
\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics{img/hist_kir_fishing.pdf}
	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{img/fishing_raster.png}
\caption{\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels. Color corresponds to \% of total fishing effort in each panel. Red polygons show LSMPAs in the region.}
\end{figure}

@@

\section{Palau National Marine Sanctuary}\label{PNMS}

\begin{figure}
	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
	\caption{Map of the Four Protected Areas}
	\label{fig:maps}
\end{figure}

\section{Alternative Controls}
\subsection{Excluding all Chinese vessels}

@@

\section{Additional methods}

This section is divided into two main parts. First, we provide a general description of AIS data and the process of identification of vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe the subset of data used in our analysis. We also point out possible shortcomings in the data, or factors that must be considered in the analysis. We then move on to explain our empirical strategy for the identification of behavioral changes and the redistribution of fishing effort.

\input{tab/baci_n_s}

@@

%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is

@@

\input{palau_purse}

@@

\input{palau_long}

>>>>

We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}). Treated vessels traveled less, with fishing events occurring closer to shore and closer to port following PIPA implementation. These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$). We do not observe a statistically significant increase in fishing hours on the high seas. This suggests that treated vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters. In summary, vessels that used to fish in PIPA are now fishing less in both Kiribati and the PNA region. Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters.

@@

The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy VDS from PNA countries. To quantify the potential impacts of this leakage, we estimate the total annual Vessel-Days received by all PNA countries by each group of vessels (Fig. \ref{fig:all_PS_VDS_year}). In this case we look at all 313 vessels, but continue to group them as treated (n = 64) and control (n = 28) vessels, as well as other vessels (n = 221). We find that the treated vessels spent 2,310 less days in Kiribati waters when comparing their values for 2015 and 2016 (Fig. \ref{fig:included_PS_VDS_year_DiD}). The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD if we use an average price of \$12,000 USD per vessel-day.\footnote{The Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report states that ``Days are currently selling in a range between \$9,000 and \$13,000.''} Looking at the total annual vessel-days allocated by all vessels to all countries, we see that the largest reductions occur for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig. \ref{fig:all_PS_VDS_cty_year}). Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allocation to PNA waters at just 10,026 vessel-days. This is 2,526 vessel-days lower (approximately \$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}). % Do you think we need to come up with an identification strategy for this?. I think a simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort, right? Current DiD estimate of these data suggests a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects. These values would represent forgone profits of 104 to 88 million USD. Again, this is if the treated vessels were allowed to maintain an upward sloping trend as observed with the control. I am also not sure if this trend is true, or just an artifact of GFW. Could we de-trend it first so that both lines are flat before, and only treated vessels show a decrease? In that setting we can then do a DiD and calculate the gap more accurately.

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_year.pdf}
	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by treated, control, and excluded vessels.}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.}
\end{figure}

We complement our analysis of change in observed vessel-days by looking at country-level data. Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig. \ref{fig:revenues}A). We find that by 2016, Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD. We then calculate total annual revenues to all PNA members (Fig. \ref{fig:revenues}B).

\begin{figure}
\centering
	\includegraphics{img/revenues.pdf}
	\caption{\label{fig:revenues}
		License revenue for PNA countries. A) Annual revenue from fishing license fees by country and year (2008 - 2016) B) The natural lof of FFA-reported revenues vs. the natural log of revenues inferred from vessel activity observations (2012 - 2016). The dashed line represents line of best fit, solid line represents 1:1 line. The same graph using absolute values is shown in the Appendix.}
\end{figure}

Catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig. \ref{fig:catches}). Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease). Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%). In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in catch over the same period.

@@

Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort. We find a crowding effect after the implementation of the protected area. Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners. 
But there is considerable redistribution of effort across space and within the fleet of purse seiners. Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
Our analysis suggests that vessels that fish elsewhere represent a loss in revenues of around \$27.7 million USD to Kiribati. A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD. Here, we discuss the implications of our findings and possible shortcomings in our analysis.

@@

A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately are the factors that guide the decision-making process of profit-maximizing agents. Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.

\begin{comment}
An additional factor that we are yet to test is the change in non-fishing hours spent at sea. It is plausible that fishing hours remain constant, but vessels have to increase search time. Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch. Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours. However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.
\end{comment}

A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in losses to countries that have been receiving revenue from granting fishing access. We also show that spatial closures lead to crowding effects, which causes some vessels to redistribute to areas close by. While LSMPAs can provide a wide range of benefits, their implementation must be accompanied with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable financing mechanisms that would compensate losses and incentivize marine conservation.

@@

Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels. These broadcast messages can be received by satellites and land-based antennas. GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \citep{kroodsma_2018}.

@@

\subsection{Analysis}

@@

\begin{figure}[H]
	\begin{align}
	y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \epsilon_t
	\label{eqn:sp_corr}
	\end{align}
\end{figure}

We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month. 
We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off. For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by centering our time series of crowding indices on the day of implementation. Our explanatory variable is therefore the number of months ($M$) before or after the implementation. For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1. Note that we restrict the sample to our treated and control vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.

@@

We attempt to identify the response of vessels to the PIPA closure. We use daily fishing and non-fishing hours, daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest. We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.

Our main specification is the following:

@@

\noindent where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$. A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group. $\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between treated and control groups, and $\beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect. Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.

\begin{comment}
We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
\end{comment}

@@

We obtained information on license fee revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report. For countries in the PNA, we assume that all license fee revenue is coming from the sale of VDS.

@@

\begin{figure}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. Countries that belong to the PNA are shown in blue, while empty polygons indicates all others. A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA. Land masses are shown in gray.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{img/all_panels.pdf}
\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas. Dashed vertical lines indicate the addition of new AIS satellites. Solid vertical line indicates the closure of PIPA.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics{img/hist_kir_fishing.pdf}
	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}

	\begin{comment}
	I would drop 2012 and 2013 and restrict 2014 to post-satellite.
	\end{comment}

\end{figure}

@@

\begin{figure}
\centering
\includegraphics{img/fishing_raster.png}
\caption{\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels. Color corresponds to \% of total fishing effort in each panel. Red polygons show LSMPAs in the region.}

\begin{comment}
Eventually we need to make a figure that shows treated minus control effort and maybe just compare 2013 with 2017 (or 2012-2014 average with 2015-2018 average).
\end{comment}

\end{figure}

@@

\section{Alternative Controls}

\begin{comment}
Need to update the captions on all the tables that follow, especially number of outcome variables, names of outcome variables, and heteroskedasticity.
\end{comment}

\subsection{Excluding all Chinese vessels}

@@

@@

%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federated States of Micronesia agreements.} However, the most notable regulation is

@@

@@

### 2019-05-30 docs/slides/GainesLab_presentation.Rmd
Added all files

@@

- 10-patch model of the tuna purse-seine fishery

@@

$$\pi_i(E_i) = pqX_i\Omega_i- \beta cE_i^{\beta-1}$$

@@

```{r}
knitr::include_graphics(here("docs", "slides", "img", "cost_no_trading.png"))
```

@@

```{r}
knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading_long_axis.png"))
```

@@

```{r}
knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading.png"))
```

@@

## Likely costs to Palau

>>>>

```{r, out.width = "250px"}
knitr::include_graphics("../img/PNA_map.png")
```

@@

- 10-patch spatial bioeconomic model of the tuna fishery

@@

$$\pi_i = pqX_i\Omega_i- \beta cE_i^{\beta-1}$$

@@

```{r, out.height = "200px"}
knitr::include_graphics(here("docs", "slides", "img", "cost_no_trading.png"))
```

@@

```{r, out.height = "200px"}
knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading_long_axis.png"))
```

@@

```{r, out.height = "200px"}
knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading.png"))
```

@@

## Likely costs to Palau (2018)

### 2019-05-30 docs/tab/DID_without_PNA.tex
Added all files

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\hline \\[-1.8ex] 
 Constant & 2.637$^{***}$ & 3.247$^{***}$ & 0.404$^{***}$ & 5.016$^{***}$ & 13.177$^{***}$ & 12.684$^{***}$ & 3.259$^{***}$ & 4.096$^{***}$ \\ 
  & (0.042) & (0.021) & (0.011) & (0.044) & (0.028) & (0.025) & (0.270) & (0.206) \\ 
  & & & & & & & & \\ 
 Post & 0.283$^{***}$ & $-$0.443$^{***}$ & 0.048$^{***}$ & 0.628$^{***}$ & 0.164$^{***}$ & 0.077$^{***}$ & 1.347$^{***}$ & 1.586$^{***}$ \\ 
  & (0.039) & (0.021) & (0.011) & (0.044) & (0.024) & (0.022) & (0.234) & (0.188) \\ 
  & & & & & & & & \\ 
 Treated & $-$0.091$^{**}$ & $-$0.051$^{***}$ & $-$0.052$^{***}$ & 0.683$^{***}$ & 0.137$^{***}$ & $-$0.020 & 0.697$^{***}$ & 0.477$^{***}$ \\ 
  & (0.040) & (0.019) & (0.011) & (0.041) & (0.024) & (0.022) & (0.233) & (0.184) \\ 
  & & & & & & & & \\ 
 Post $\times$ Treated & 0.081$^{*}$ & 0.021 & 0.055$^{***}$ & $-$0.880$^{***}$ & $-$0.153$^{***}$ & 0.017 & $-$0.691$^{***}$ & $-$0.706$^{***}$ \\ 
  & (0.042) & (0.023) & (0.011) & (0.046) & (0.027) & (0.024) & (0.251) & (0.202) \\ 
  & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 19,971 & 42,555 & 19,971 & 43,068 & 19,971 & 19,971 & 1,207 & 1,696 \\ 
R$^{2}$ & 0.064 & 0.097 & 0.066 & 0.032 & 0.059 & 0.071 & 0.133 & 0.217 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\begin{table}[H] \centering 
  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 9 variables of interest after removing PNA vessels: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
\hline \\[-1.8ex] 
 Constant & 0.512$^{***}$ & 3.559$^{***}$ & 0.083$^{***}$ & 4.499$^{***}$ & 13.165$^{***}$ & 12.667$^{***}$ & 3.271$^{***}$ & 4.066$^{***}$ & 2.876$^{***}$ \\ 
  & (0.024) & (0.013) & (0.004) & (0.047) & (0.028) & (0.025) & (0.263) & (0.201) & (0.434) \\ 
  & & & & & & & & & \\ 
 Post & 0.781$^{***}$ & $-$0.159$^{***}$ & 0.122$^{***}$ & 0.047 & 0.114$^{***}$ & 0.070$^{***}$ & 1.168$^{***}$ & 1.481$^{***}$ & 0.295 \\ 
  & (0.022) & (0.012) & (0.004) & (0.043) & (0.023) & (0.022) & (0.226) & (0.180) & (0.333) \\ 
  & & & & & & & & & \\ 
 Displaced & 0.202$^{***}$ & 0.040$^{***}$ & 0.019$^{***}$ & 0.437$^{***}$ & 0.165$^{***}$ & $-$0.015 & 0.817$^{***}$ & 0.533$^{***}$ & $-$0.408$^{*}$ \\ 
  & (0.015) & (0.009) & (0.003) & (0.037) & (0.024) & (0.022) & (0.229) & (0.182) & (0.235) \\ 
  & & & & & & & & & \\ 
 NINO4 & $-$0.019 & $-$0.0003 & $-$0.002 & $-$0.387$^{***}$ & 0.138$^{***}$ & 0.025$^{***}$ & 0.413$^{***}$ & 0.232$^{***}$ & 0.482$^{***}$ \\ 
  & (0.012) & (0.006) & (0.002) & (0.020) & (0.010) & (0.009) & (0.080) & (0.066) & (0.156) \\ 
  & & & & & & & & & \\ 
 Post $\times$ Displaced & $-$0.219$^{***}$ & $-$0.055$^{***}$ & $-$0.023$^{***}$ & $-$0.246$^{***}$ & $-$0.175$^{***}$ & 0.010 & $-$0.843$^{***}$ & $-$0.821$^{***}$ & 0.729$^{**}$ \\ 
  & (0.024) & (0.012) & (0.004) & (0.046) & (0.026) & (0.024) & (0.243) & (0.195) & (0.341) \\ 
  & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 64,560 & 64,560 & 64,559 & 64,625 & 22,654 & 22,654 & 1,366 & 1,928 & 511 \\ 
R$^{2}$ & 0.093 & 0.069 & 0.099 & 0.022 & 0.063 & 0.066 & 0.127 & 0.203 & 0.214 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
